\chapter{Defining the problem}

\section{Predict whether salary exceeds 50,000}
Prediction task is to determine whether a person makes over 50K a year by given data for his social background. 

\section{History of the dataset}
Extraction was done by Barry Becker from the 1994 Census database
The dataset has 48,882 instances, 14 attributes, has missing values and our problem is a class

\section{Attribute information}
The dataset contains the following attributes about a person ~\cite{uci-link}:
\begin{enumerate}
    \item Age - continuos
    \item Workclass - Private, Self-emp-not-inc, Self-emp-inc, Federal-gov, Local-gov, State-gov, Without-pay, Never-worked.
    \item Fnlwgt - sample weighting; this should be ignored while creating models
    \item Education - Bachelors, Some-college, 11th, HS-grad, Prof-school, Assoc-acdm, Assoc-voc, 9th, 7th-8th, 12th, Masters, 1st-4th, 10th, Doctorate, 5th-6th, Preschool. 
    \item Education-num: continuous (how many years has one learned)
    \item Marital status: Married-civ-spouse, Divorced, Never-married, Separated, Widowed, Married-spouse-absent, Married-AF-spouse. 
    \item Occupation: Tech-support, Craft-repair, Other-service, Sales, Exec-managerial, Prof-specialty, Handlers-cleaners, Machine-op-inspct, Adm-clerical, Farming-fishing, Transport-moving, Priv-house-serv, Protective-serv, Armed-Forces.
    \item Relationship: Wife, Own-child, Husband, Not-in-family, Other-relative, Unmarried. 
    \item Race: White, Asian-Pac-Islander, Amer-Indian-Eskimo, Other, Black. 
    \item Sex: Female, Male. 
    \item Capital gain: continuous, how much an individual has learned outside his usual wage
    \item Capital loss: continuous, how much an individual has lost outside his usual wage.
    \item Hours per week: continuous, how many hours per week an individual works
    \item: Native country: United-States, Cambodia, England, Puerto-Rico, Canada, Germany, Outlying-US(Guam-USVI-etc), India, Japan, Greece, South, China, Cuba, Iran, Honduras, Philippines, Italy, Poland, Jamaica, Vietnam, Mexico, Portugal, Ireland, France, Dominican-Republic, Laos, Ecuador, Taiwan, Haiti, Columbia, Hungary, Guatemala, Nicaragua, Scotland, Thailand, Yugoslavia, El-Salvador, Trinadad and Tobago, Peru, Hong, Holand-Netherlands.
\end{enumerate}
\section{First look at the dataset}
There are a lot more examples from the first class (<50k earnings). 

\chapter{Analyze the data}
\section{Handling missing values}
\section{Balancing classes}
\section{Normalization and standardization}
\section{Descriptive statistics}

\chapter{Prepare data}
\section{Raw view of the dataset}
\section{Normalized view of the dataset}
\section{Standardized view of the dataset}
\section{Dataset after feature selection}

\chapter{Evaluate algorithms}
\section{Initial experiment design}

\chapter{Impove results}
\section{Experiment for improving result}

\chapter{Present results}